---
title: "Barbituate 1"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output:
  workflowr::wflow_html:
    toc: false
---


```{r results='hide', message=FALSE, warning=FALSE}

rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
library('tidyverse')

#dataset="_rr"
dataset=""

get_data_from_cache(df_suffix = dataset)
intersect_filename = paste0( 'data/df_intersect', dataset, '.rdata')


df %<>% mutate( row=row_number())

df %>%
  filter( is_benzo( type_code ) ) %>%
  { . } -> df_benzo


df %>%
  filter( !is_benzo( type_code ) ) %>%
  { . } -> df_opioid

df_patient_opioid = df_patient %>% filter( pin %in% df_opioid$pin)
df_patient_benzo = df_patient %>% filter( pin %in% df_benzo$pin)


```

#Dataset summary


```{r data_summary, echo=FALSE, warning=FALSE, results='asis'}
cat("  \n###",  "Total Number of Scripts with either Benzo or Opioid\n")
df %>%group_by(state) %>% count()
#
cat("  \n###",  "Total Number of People with either Benzo or Opioid\n")
df_patient %>%group_by(state) %>% count()
#
cat("  \n###",  "Total Number of People with Opioid \n")
print('people')
df_patient_opioid %>%group_by(state) %>% count()

```

#Methods  - find overlaps 
##Condervative Assumptions 
  * 7 day window at start and end of opioid presciption
  * 2 doses / day

```{r generate_benzo, warning=FALSE}

if (file.exists( intersect_filename )) {
  load( intersect_filename, verbose=TRUE )
} else {
#

  df %>%
    filter( is_benzo( type_code ) ) %>%
    group_by(pin) %>%
    mutate( end_date = supply_date + floor(quantity/2)) %>%
    select( pin, item_code, quantity, n_dose, supply_date, end_date, row) %>% 
    nest( item_code, supply_date, end_date, quantity, n_dose, row, .key=benzo ) %>%
    { . } -> df_benzo_nested
#
  df %>%
    filter( !is_benzo( type_code ) ) %>%
    group_by(pin) %>%
    mutate( end_date = supply_date + floor(quantity/2)) %>%
    select( pin, item_code, quantity, n_dose, supply_date, end_date, row) %>% 
    nest( item_code, supply_date, end_date, quantity, n_dose, row, .key=opioids ) %>%
    { . } -> df_opioid_nested
#
  library('IRanges')

#
#
#  df_benzo_nested %>%
#    inner_join( df_opioid_nested ) %>% 
#    rowwise() %>%
#    do( joined =  interval_inner_join( .$opioids, .$benzo, by=qw('supply_date end_date') )) %>%
#    ungroup() %>%
#    cbind( df_both ) %>%
#    as.tibble() %>%
#    select(pin, joined ) %>%
#    unnest() %>%
#    { . } -> df_intersect
#
#

  cluster <- create_cluster(4)
  df_benzo_nested %>%
    inner_join( df_opioid_nested ) %>% 
    partition(pin, cluster=cluster )  %>%
    { . } -> df_both
#
  cluster_library(df_both, c("tidyverse", "IRanges", "fuzzyjoin"))
#

  df_both %>%
    do( joined = interval_inner_join( data.frame(.$opioids), 
                                     data.frame(.$benzo), 
                                     by=c('supply_date','end_date') ))  %>%
      collect() %>%
      ungroup() %>%
      unnest() %>% 
      mutate( supply_year = year( supply_date.x)) %>%
      { . } -> df_intersect
#

  save(df_intersect, file=intersect_filename)

}

#cl <- makeCluster("thealfred.duckdns.org", user="dewoller", master="131.172.55.229", homogeneous=FALSE)

 ```

#What do the group of double dippers look like
We need to have some measure of dd intensity, we could use:
  * compare them with the single dippers, e.g. as percentage of single opioid users
  * on their own, e.g by DDD, or by # of days of overlap

##Questions
  * how to normalise data;  
  * further research questions;  what about users that overlap with their own opioid prescriptions

```{r explore_overlap, warning=FALSE}


df_intersect %>% 
  distinct(pin) %>%
  inner_join(df_patient) %>%
  ggplot(aes(age, fill=sex)) + geom_bar() +
  ggtitle( "Number of double dippers by gender and age group")

df_intersect %>% 
  distinct(pin) %>%
  inner_join(df_patient_usage) %>%
  inner_join(df_patient) %>%
  ggplot(aes(age, fill=usage_category)) + geom_bar() +
  ggtitle( "Number of double dippers by opioid usage_category and age group")

df_intersect %>% 
  inner_join(df_patient_usage %>% filter( drug_type=='opioid')) %>%
  inner_join(df_patient) %>%
  ggplot(aes(supply_year, fill=usage_category)) + geom_bar() +
  ggtitle( "Number of double dippers by opioid usage_category and supply_year")

df%>% 
  ggplot(aes(supply_year, fill=drug_type)) + 
  geom_bar() +
  ggtitle( "Number of benzo and/or opioid scripts by supply_year")


```

# what type of users do we have
### number of users of each type, overall

df %>%
group_by( usage_type, type_name) %>%
summarise(  quantity=sum(quantity) ) %>%
ggplot( aes( usage_type, quantity, fill=type_name)) +
geom_col()+ 
ggtitle( "Total number of pills per usage and drug type")

```{r, warning=FALSE, echo=FALSE}

df_patient %<>%
  mutate( is_benzo_user = (pin %in% df_patient_benzo$pin),
         user_type = as.factor(
                      ifelse( pin %in% df_intersect$pin, 
                            '2_double-dipper', 
                      ifelse( is_benzo_user & (pin %in% df_patient_opioid$pin), 
                              '2_seperate_times', 
                        ifelse( is_benzo_user, 
                               '1_benzodiazapine', 
                               '1_opioid')))))


df_patient %>%
  ggplot( aes(sex, fill=user_type)) +
  geom_bar()+ 
  ggtitle( "Number of benzo only, opioid only, and both users ") +
  facet_wrap( ~age ) 

```

### Prescriptions that participate in double dipping

```{r, warning=FALSE}

df %<>% mutate( usage_type = as.factor(
                                    ifelse( row %in% df_intersect$row.x,
                                    'opioid_dd',
                                    ifelse(  row %in% df_intersect$row.y,
                                    'benzo_dd', 
                                    paste( drug_type, 'alone') ))))

df %>%
  group_by( usage_type, type_name) %>%
  summarise(  quantity=sum(quantity) ) %>%
  ggplot( aes( usage_type, quantity, fill=type_name)) +
  geom_col()+ 
  ggtitle( "Total number of pills per usage and drug type")

df %>%
  group_by( usage_type, supply_year) %>%
  summarise(  quantity=sum(quantity) ) %>%
  ggplot( aes( supply_year, quantity, color=usage_type, group=usage_type)) +
  geom_line()+ 
  ggtitle( "Total number of pills per usage and year")

```









