---
title: "Population Exploration"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-11-19 "
output:
  workflowr::wflow_html:
    toc: false
---

```{r pre_initial, echo=FALSE, results='hide', message=FALSE, warning=FALSE}

rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/standardisation.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
source("lib/findOverlap.R")
library('tidyverse')
opts_chunk$set(echo = FALSE)

```


```{r initial, results='hide', message=FALSE, warning=FALSE}

dataset="_rr"
dataset=""
get_data_from_cache(dataset = dataset)
#source('lib/findOverlap_simplified.R')

```


```{r generate_continuing_users }
#



```{r replicate }



```



```{r get_continuing_users}

cat ('# number of users who do not double dip ')

df_match %>%
  count( is_dd ) 

cat ('# ratio of double dippers for each usage category')

df_match %>% 
  count( usage_category, is_dd) %>% 
  spread( is_dd, n ) %>%
  mutate( ddpct = dd/(not_dd + dd) )


df_match %>% 
  inner_join( df_patient ) %>%
  count( lga, usage_category, is_dd) %>% 
  spread( is_dd, nn ) %>%
  mutate( ratio_dd = dd/not_dd ) %>%
  filter( lga != '.' ) %>%
  filter( usage_category == 'regular') %>%
  right_join( df_population %>% distinct( lga ) ) %>%
  mutate( ratio_dd = ifelse( is.na( ratio_dd), 0, ratio_dd )) %>%
  mutate( value = cut( ratio_dd, 
                    breaks=quantile( ratio_dd, probs=seq(0,1,1/3) ), 
                    labels=qc( low, medium, high ))
  ) %>%
  mutate( value = factor( ifelse( is.na( value ), 1, value ),
                         labels=qc( low, medium, high )  )) %>%
  print_map( title="Ratio between dd and regular users", filename='/tmp/dd_regular.png', inset_states=c(1,2,4:6 ) ) -> a
  

df_match %>% 
  inner_join( df_patient ) %>%
  count( lga, usage_category, is_dd) %>% 
  spread( is_dd, nn ) %>%
  mutate( ratio_dd = dd/not_dd ) %>%
  filter( lga != '.' ) %>%
  filter( usage_category == 'one-off') %>%
  right_join( df_population %>% distinct( lga ) ) %>%
  mutate( ratio_dd = ifelse( is.na( ratio_dd), 0, ratio_dd )) %>%
  mutate( value = cut( ratio_dd, 
                      breaks=quantile( ratio_dd, probs=seq(0,1,1/3) ), 
                      labels=qc( low, medium, high ))
  ) %>%
  mutate( value = factor( ifelse( is.na( value ), 1, value ),
                         labels=qc( low, medium, high )  )) %>%
  print_map( title="Ratio between dd and one-off users", filename='/tmp/dd_one-off.png', inset_states=c(1,2,4:6 ) ) -> a
```

```{r prediction_dd}
library( caret )


df_match %>% 
  mutate( ndays = ifelse( is.na( ndays ), 0, ndays )) %>%
  inner_join( df_patient ) %>%
  select( -state, -pin) %>%
  inner_join( df_population %>% 
             filter( supply_year=='2013' ) %>%
             group_by( lga, seifa, urbanization, state, irsd_score_raw, area_albers_sqkm ) %>% 
             summarise( population = sum( population) , density=sum( population ) / min(area_albers_sqkm)) , 
           by='lga') %>% 
  mutate( is_dd = factor( is_dd ),  
         state = factor( get_state_code_from_lga( lga) ),
         sex=as.factor( sex )
         ) %>%
  select( -drug_type, -lga, -area_albers_sqkm ) %>%
  drop_na() %>%
  { . } -> df_prediction

df_prediction %>%
  select(-ndays) %>% 
  { . } -> df_prediction1
#
intrain <- createDataPartition(y =  df_prediction$is_dd, p= 0.7, list = FALSE)
training <- df_prediction[intrain,]
testing <- df_prediction[-intrain,]
ctrl <- trainControl(method = "repeatedcv",
                     number = 10,
                     repeats = 5,
                     summaryFunction = twoClassSummary,
                     classProbs = TRUE)

rf_fit <- train(is_dd ~ .,
                data = training, 
                method = "gbm",
                trControl=ctrl, 
                verbose=TRUE,
                metric='ROC'
                )
#
#

rf_fit 

test_roc <- function(model, data) {
  
  roc(data$is_dd,
      predict(model, data, type = "prob")[, "not_dd"])

}

rf_fit %>% predict( data=testing, type='prob') -> a

library(gbm)
pretty.gbm.tree(rf_fit$finalModel,i.tree = 1)

rf_fit %>% 
  predict( data=testing) %>%
  as.tibble() %>% 
  { . } ->prediction

rf_fit %>% 
  test_roc(data = testing) %>%
  auc()
 
#
confusionMatrix( factor(testing$is_dd), prediction )

#preProcess=  c("center", "scale", "YeoJohnson", "nzv", "pca")

rf_fit$finalModel

plot( rf_fit )
varImp( rf_fit$finalModel )

 

```


```{r multilevel_modelling}

foreign::read.dta( 'data/nobackup/match_multiyear.v2.dta' ) %>%
  as.tibble() %>% 
  { . } -> df_match


foreign::read.dta( 'data/nobackup/match_single_period.v1.dta' ) %>%
  as.tibble() %>% 
  { . } -> df_match_1


df_match_1  %>%
  mutate( 
         is_dd = ifelse( ndays ==0, 0, 1 ), 
         sex = factor( sex ), 
         age = factor( age ), 
         lga = factor( lga ), 
         state_name = factor( state_name ), 
         seifa = factor( seifa ), 
         urbanization = factor( urbanization ), 
         sex = relevel( sex, ref=2),
         seifa = relevel( seifa, ref=4),
         urbanization = relevel( urbanization, ref=2) ) %>% 
  { . } -> df_match_1





library( lme4 )
    
df_match_1 %>% 
lme4::glmer( is_dd ~ age + sex + seifa + urbanization + (1|lga) + (1|state_name), 
            data=., 
            family = binomial,
            control=glmerControl(optimizer="bobyqa")
            )->d

exp( fixef( d ))




```


```{r multi_level_model_with_quantiity }

df %>%
  group_by( pin, drug_type ) %>%
  summarise( n_dose = sum( n_dose ) ) %>% 
  { . } -> df_doses


df_doses %>%
  spread( drug_type, n_dose ) %>%
  mutate( b_dose  = ifelse( is.na( benzodiazepine ), 0, benzodiazepine ),
         o_dose  = ifelse( is.na( opioid ), 0, opioid ) ) %>%
  select( -benzodiazepine, -opioid ) %>% 
  { . } -> df_dose1

df_match_1 %>%
  mutate( 
         is_dd = ifelse( ndays ==0, 0, 1 ), 
         sex = factor( sex ), 
         age = factor( age ), 
         lga = factor( lga ), 
         state_name = factor( state_name ), 
         seifa = factor( seifa ), 
         urbanization = factor( urbanization ), 
         sex = relevel( sex, ref=2),
         seifa = relevel( seifa, ref=4),
         urbanization = relevel( urbanization, ref=2) ) %>% 
   inner_join( df_dose1, by='pin') %>%
   mutate( doses = scale( o_dose + b_dose ) ) %>%
   lme4::glmer( is_dd ~ doses+age + sex + seifa + urbanization + (1|lga) + (1|state_name), 
              data=., 
              family = binomial,
              control=glmerControl(optimizer="bobyqa")
              )->d



```


```{r xtmelogit_comparision}


library(lme4)

read.csv( url( "https://stats.idre.ucla.edu/stat/data/hdp.csv")) %>%
  as.tibble() %>% 
  { . } -> hdp

hdp %>%
  mutate( remission=factor( remission )) %>% 
  { . } -> hdp


glmer( remission ~ IL6+ CRP +CancerStage+LengthofStay+Experience+ (1|DID), 
        data=hdp, 
        family=binomial
        ) %>% 
        { . } -> glmer_hdp_remission1
 
      exp( fixef( glmer_hdp_remission1))


glmer( remission ~ Age + LengthofStay+ FamilyHx + IL6+ CRP +CancerStage+Experience+ (1|HID) + (1|DID), 
      data=hdp, 
      family=binomial
      ) %>% 
{ . } -> glmer_hdp_remission2

 
```
