---
title: "Population Exploration"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-11-19 "
output:
  workflowr::wflow_html:
    toc: false
---

```{r pre_initial, echo=FALSE, results='hide', message=FALSE, warning=FALSE}

rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/standardisation.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
#source("lib/findOverlap.R")
source("lib/mapping_functions.R")
library('tidyverse')
opts_chunk$set(echo = FALSE)

```
# sanity checking;  a person only has 1 state
with a as (
  SELECT distinct pin, state 
  from continuing.continuing
  ) 
  select pin, state, count( pin )
  from a
  group by 1, 2
  having count( distinct state ) > 1

```{r initial, results='hide', message=FALSE, warning=FALSE}

dataset="_rr"
dataset=""
get_data_from_cache(dataset = dataset)
#

foreign::read.dta( 'data/nobackup/match_multiyear.v2.dta' ) %>%
  as.tibble() %>% 
  { . } -> df_match


tic( 'join')
df%>%
  filter( drug_type == 'opioid' ) %>%
  inner_join( df%>% filter( drug_type == 'benzodiazepine' ) %>% select( pin, supply_date ), 
             by=qc( pin, supply_date )) %>% 
  mutate( supply_year = as.character( year(supply_date))) %>%
  { . } -> df_dd_0
toc()
################# ################# ################# ################# 
```
# section 1
## same day distinct double dip episodes by sex and year
```{r}


df_dd_0 %>%
  distinct( pin, supply_date, supply_year) %>%
  inner_join( df_patient ) %>%
  count( sex, supply_year ) %>%
  group_by( supply_year ) %>%
  mutate( percent = round( n/sum(n) * 100 , 2 )) %>%
  ungroup() %>%
  gather( type, value, -sex, -supply_year ) %>% 
  spread( sex, value )


```

## same day distinct double dip episodes by year totals
```{r}

df_dd_0 %>%
  distinct( pin, supply_date, supply_year) %>%
  inner_join( df_patient ) %>%
  count( supply_year ) 

```

## same day distinct double dip episodes by sex totals

```{r}
df_dd_0 %>%
  distinct( pin, supply_date, supply_year) %>%
  inner_join( df_patient ) %>%
  count( sex )  %>% 
  mutate( percent = round( n/sum(n) * 100 , 2 )) 



```

# section 3

## same day distinct double dip episodes by age and year
```{r}


df_dd_0 %>%
  distinct( pin, supply_date, supply_year) %>%
  inner_join( df_patient ) %>%
  count( age, supply_year ) %>%
  group_by( supply_year ) %>%
  mutate( percent = round( n/sum(n) * 100 , 2 )) %>%
  ungroup() %>%
  gather( type, value, -age, -supply_year ) %>% 
  spread( age, value )


```

## same day distinct double dip episodes by age totals

```{r}
df_dd_0 %>%
  distinct( pin, supply_date, supply_year) %>%
  inner_join( df_patient ) %>%
  count( age )  %>% 
  mutate( percent = round( n/sum(n) * 100 , 2 )) 



```
# section 3

## same day distinct double dip people by sex

```{r}

df_dd_0 %>%
  distinct( pin, supply_year) %>%
  inner_join( df_patient ) %>%
  count( sex, supply_year ) %>%
  group_by( supply_year ) %>%
  mutate( percent = round( n/sum(n) * 100 , 2 )) %>%
  ungroup() %>%
  gather( type, value, -sex, -supply_year ) %>% 
  spread( sex, value )

```

# section 4 
##  Nextday dispensing  - not done

# section 5
## Distinct double dippers (sameday and ddd overlap)
### totals by year

```{r}

df_match %>% 
  filter( ndays > 0 )  %>%
  count( supply_year )

df_match %>% 
  filter( ndays > 0 )  %>%
  count( supply_year ) %$%
  sum(n)


```

### distinct individuals

```{r}

df_match %>% 
  filter( ndays > 0 )  %>%
  distinct( pin ) %>%
  count(  )


```

### distinct individuals  by sex

```{r}

df_match %>% 
  filter( ndays > 0 )  %>%
  count( supply_year, sex ) %>%
  spread( sex, n )


```

### distinct individuals by age and sex

```{r test}

df_match %>% 
  filter( ndays > 0 )  %>%
  count( supply_year, sex, age ) %>%
  mutate( age_sex = paste0(sex, '-', age )) %>%
  select( -age, -sex) %>%
  spread( age_sex, n )


```
### distinct male and female by state

```{r}

df_match %>% 
  filter( ndays > 0 )  %>%
  count( supply_year, state) %>%
  spread( state, n )


```
# section 6
## Total episode of utilisation
### totals scripts overall

```{r}

df %>% 
  count( drug_type ) %>%
  mutate( pct = round( n/sum(n) * 100, 2 ))

```
### drug of preference

```{r}

df %>% 
  distinct( pin, drug_type ) %>%
  group_by( pin ) %>%
  arrange( pin, drug_type ) %>%
  summarise( dt1 = paste( drug_type, collapse=',')) %>%
  count( dt1 )

```

# section 7
### 2 step standardised dd people per 1000
Standardized double dippers from Dennis (through two step standandization) that is standdizing the LGAs first and then taking the average 

```{r}

df_match %>% 
  filter( ndays > 0 )  %>%
  filter( lga != '.' ) %>%
  count( supply_year, lga, age, sex ) %>%  
  simple_standardise_value( group_by_vars=qc(lga, supply_year) ,  count_var='n' ) %>%
  mutate( rate = rate * 10 ) %>%
  inner_join( select( df_population, lga, state )) %>%
  group_by( supply_year, state ) %>%
  summarise( rate = mean( rate )) %>%
  spread( state, rate )


```

# section 7
### 2 step standardised dd number of days per 1000 people
Standardized double dippers from Dennis (through two step standandization) that is standdizing the LGAs first and then taking the average 

```{r}

df_match %>% 
  filter( ndays > 0 )  %>%
  filter( lga != '.' ) %>%
  group_by( supply_year, lga, age, sex ) %>%  
  summarise( ndays = sum( ndays ) ) %>%
  simple_standardise_value( group_by_vars=qc(lga, supply_year) ,  count_var='ndays' ) %>%
  mutate( rate = rate * 10 ) %>%
  inner_join( select( df_population, lga, state )) %>%
  group_by( supply_year, state ) %>%
  summarise( rate = mean( rate )) %>%
  spread( state, rate )


```

# section 8
## These are yearwise episode (taking DDD and oneday together)?? Pls double check

```{r}

df_match %>% 
  filter( ndays > 0 )  %>%
  group_by( supply_year, pin) %>%  
  summarise( ndays = sum( ndays ) ) %>%
  ungroup() %>%
  group_by( supply_year) %>%
  summarise( n = n(), 
            total_days = sum( ndays ),  
            mean = mean(ndays),
             sd = sd( ndays ), 
             min = min( ndays ),
             max = max( ndays )
  )


  
```

## 

```{r}




```

## 

```{r}


