---
title: "Population Exploration,rf"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output:
  workflowr::wflow_html:
    toc: false
---

```{r pre_initial, echo=FALSE, results='hide', message=FALSE, warning=FALSE}

rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/standardisation.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
source("lib/findOverlap.R")
library('tidyverse')
opts_chunk$set(echo = FALSE)

```


```{r initial, results='hide', message=FALSE, warning=FALSE}

dataset="_rr"
dataset=""
get_data_from_cache(dataset = dataset)
source('lib/findOverlap_simplified.R')



# standardise test
df_opioid %>%
  inner_join( df_benzo, by = qc( pin, supply_date )) %>%
  distinct( supply_date, pin ) %>%
  mutate( supply_year = as.character( year( supply_date ))) %>%
  left_join( df_patient, by='pin' ) %>%
  count( supply_year, state, age, sex ) %>% 
  { . } -> df_standardise

df_standardise %>%
  summarise( sum( n ))

  simple_standardise_value( 
                           
                          
                           group_by_vars=qc(state, supply_year) 
                           
                           ,  
                           count_var='n' 
                           ) %>%
  mutate( rate = rate * 10 ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  spread( state, rate) %>% tableHTML::tableHTML() %>% clipr::write_clip()

# end test


```


```{r test_same_day  }

df_opioid %>%
  inner_join( df_benzo, by = qc( pin, supply_date )) %>%
  distinct( supply_date, pin ) %>%
  mutate( supply_year = as.character( year( supply_date ))) %>%
  left_join( df_patient, by='pin' ) %>%
  count( supply_year, state, age, sex ) %>%
  simple_standardise_value( group_by_vars=qc(state, supply_year) ,  count_var='n' ) %>%
  mutate( rate = rate * 10 ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  spread( state, rate) %>% tableHTML::tableHTML() %>% clipr::write_clip()


```


```{r test_same_day_way2 }



df_dd_0_new %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  # count distinct people and date of supply
  distinct( age, sex, pin, state, supply_year, supply_date.benzo ) %>%
  count( supply_year, state, age, sex ) %>%
  simple_standardise_value( group_by_vars=qc(state, supply_year) ,  count_var='n' ) %>%
  mutate( rate = rate * 10 ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  spread( state, rate) %>% tableHTML::tableHTML() %>% clipr::write_clip()

```


```{r total_population_by_state }



df_population %>%
  group_by( supply_year, state ) %>%
  summarise( population = sum( population )) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  print()

#df %>% distinct( pin )

```


```{r distinct_pp_0day }


df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  distinct( pin ) %>% count()


```


```{r overall_ }

df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  distinct( pin, supply_year ) %>% count()

df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  filter( lga != '.' ) %>%
  distinct( state, pin, supply_year ) %>% 
  count( state, supply_year )

df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  summary( lga)


df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  distinct( age, sex, pin, state) %>%
  count( state) %>%
  summarise( sum(n ))

df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  distinct( age, sex, pin, state, supply_year) %>%
  count( supply_year, state, age, sex ) %>%
  summarise( sum(n ))



# state level standardisation
df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  filter( lga != '.' ) %>%
  distinct( age, sex, pin, state, supply_year) %>%
  count( supply_year, state, age, sex ) %>%
  simple_standardise_value( group_by_vars=qc(state, supply_year) ,  count_var='n' ) %>% 
  { . } -> overall_state_rate


overall_state_rate %>% spread( state, rate) %>% xc()

# lga level standardisation

df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  distinct( age, sex, pin, lga, state, supply_year) %>%
  count( supply_year, lga, state, age, sex ) %>%
  filter( lga != '.' ) %>%
  simple_standardise_value( group_by_vars=qc(lga, state, supply_year) ,  count_var='n' ) %>% 
  { . } -> by_lga


by_lga %>%
  spread( supply_year, rate) %>% 
  xc()


# get mofi's populations

read.dta13('data/nsw_vic_populato_and_seifa_data.dta') %>% 
tbl_df() %>%
rename( lga_name = lga, 
        lga = lgacode,
        sex = sex2,
        population = populato 
        ) %>%
filter( substring( lga,1,1) <= '2') %>%
mutate( supply_year=as.character(year ),
        age = age_groups[as.integer( age4) ],
        state = ifelse( substring( lga,1,1) == '1', 'NSW', 'VIC'),
        lga = as.character(lga)
        ) %>%
select(-year, -age4, -lga_name ) %>%
mutate( seifa=ordered(seifa, levels=c('Least','Moderate','High','Very High'))) %>%
{.} -> df_population
 
