---
title: "Population Exploration,rf"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output:
  workflowr::wflow_html:
    toc: false
---

```{r pre_initial, echo=FALSE, results='hide', message=FALSE, warning=FALSE}

rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/standardisation.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
source("lib/findOverlap.R")
library('tidyverse')
opts_chunk$set(echo = FALSE)

```


```{r initial, results='hide', message=FALSE, warning=FALSE}

dataset="_rr"
dataset=""

get_data_from_cache(dataset = dataset)
source('lib/findOverlap_simplified.R')

################# ################# ################# ################# 
# data prep finished
################# ################# ################# ################# 
 
# sanity checks
setdiff( names( df_dd_overlap_all ), names( df_dd_1b_new ))
setdiff(  names( df_dd_1b_new ),names( df_dd_overlap_all ))

setdiff( names( df_dd_overlap_all ), names( df_dd_0_new ))
setdiff(  names( df_dd_0_new ),names( df_dd_overlap_all ))

anti_join( df_dd_overlap_all , df_dd_1b_new )
anti_join( df_dd_overlap_all , df_dd_1a_new )
anti_join( df_dd_overlap_all , df_dd_0_new )

anti_join(  df_dd_1b_new,df_dd_overlap_all  )
anti_join(  df_dd_1a_new,df_dd_overlap_all  )
anti_join(  df_dd_0_new,df_dd_overlap_all  )

# sanity checks
df_dd_overlap_benzo %>% count(row, sort=TRUE)
df_dd_0_new %>% count(row.benzo, row.opioid, sort=TRUE)
df_dd_0_new %>% count(row.opioid, sort=TRUE)
df_dd_0_new %>% count(row.benzo, sort=TRUE)
df_dd_overlap_combined %>% count(row.benzo, sort=TRUE)

df_dd_0_new %>% arrange( pin, supply_date.opioid, item_code.opioid ) 

df_dd_overlap_combined %>% arrange( pin, supply_date.opioid, item_code.opioid ) 
setdiff(  names( df_dd_1b_new ),names( df_dd_overlap_all ))

df_dd_overlap_combined %>% distinct ( pin, supply_year ) %>% count()
df_dd_0_new%>% distinct ( pin ) %>% count()


if (FALSE) { # test cod
  # make sure data is in supply date order
  df %>%
    group_by( pin ) %>%
    arrange( row ) %>% 
    filter( supply_date > lead( supply_date ) & pin == lead( pin ))
  # number of multiple script
  df %>%
    count( pin, supply_date, sort=TRUE ) %>%
    filter( n>1)
}

df_dd_overlap_combined  %>%
  distinct( pin, supply_year ) %>%
  left_join( df_patient ) %>% 
  { . } -> df_pat_all


df_pat_all %>% distinct( lga )  %>% arrange(lga)
  count( sex, supply_year ) %>%
  summarise( sum( n ))


df %>% distinct( lga )  %>% anti_join( df_pat_all %>% distinct( lga ) )

df %>% summarise( sum( quantity ))

```
# get mofi data
```{r}


read.dta13( '/mnt/sda5/store/aarnet_owncloud/Sharing_between_mofi_and_dennis/pick_z.dta') %>%
  as.tibble() %>% 
  rename( pin=ID,
         lga=lgacode,
         item_code=ItemCode,
         n_dose = DDD,
         quantity=qty,
         supply_date=DateSupply,
         unit_wt = Unit_wt,
         ddd_mg_factor = DDD,
         ) %>%
  mutate (
          state=str_trim( state ),
          sex=str_trim( sex ),
          age = age_grouping_mofi( age),
          lga = as.character( lga ) ,
          item_code = str_trim(item_code ), 
          n_dose=quantity * unit_wt / ddd_mg_factor ,
          supply_date= dmy( supply_date ),
          supply_year=as.character( year( supply_date))
          ) %>% 
  { . } -> mofi1


mofi1 %>% count( lga, pick_z )


# mofis 
df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  filter( lga != '.' ) %>%
  distinct( pin, lga, sex ) %>%
  bothDiff( mofi1 %>% filter( pick_ci==1 ), by='pin' )

df_dd_overlap_all  %>% distinct( pin )



df_dd_overlap_all %>%
  bind_rows( df_dd_0_new ) %>%
  mutate( supply_year = as.character( supply_year.opioid ) ) %>%
  left_join( df_patient ) %>%
  dplyr::filter( state %in% qc( NSW, VIC ) ) %>%
  distinct ( supply_year, pin )

  summary( lga)

```
# zero day differences
```{r}


mofi1 %>% 
  filter( !is.na( samedate)) %>% 
  { . } -> mofi_dd_0

df_dd_0_new %>%
  count( pin, supply_year.opioid ) %>%
  rename( supply_year=supply_year.opioid ) %>%
  bothDiff( mofi_dd_0 %>% count( pin, supply_year ), by=qc( pin, supply_year, n ))

df_dd_0_new %>%
  distinct( pin, supply_year.opioid ) %>%
  rename( supply_year=supply_year.opioid ) %>%
  bothDiff( mofi_dd_0 %>% distinct( pin, supply_year ), by=qc( pin, supply_year ))

df_dd_0_new %>%
  count( pin) %>%
  bothDiff( mofi_dd_0 %>% count( pin), by=qc( pin))



```
# single day differences
```{r}


```
# investigate individuals
```{r}



df %>% filter( pin == '90312')

mofi1 %>% filter( pin=='90312')

df %>% filter( pin == '132789')


explore = function( mpin ) {
  df %>% filter( pin == mpin ) %>% arrange( supply_date, item_code ) %>% print()
  mofi1 %>% 
    filter( pin==mpin ) %>%  
    arrange( supply_date, item_code ) %>% 
    select( Day_diff, Stnd_dose,quantity, ddd_mg_factor, unit_wt, everything()) %>%
    print()

#  df_dd_0_new %>% filter( pin == mpin) %>% print()
#  mofi_dd_0 %>% filter( pin==mpin) %>% print()

  df_dd_overlap %>% filter( pin == mpin) %>% print()
  df_dd_overlap_all %>% filter( pin == mpin) %>% print()
  mofi_dd_multi %>% filter( pin==mpin) %>% print()
  FALSE
}

explore( 3209161230)

  df %>% 
    filter( pin==5529050722) %>%  
    filter( supply_date >= '2014-07-08') %>%  
   arrange( supply_date, item_code ) %>% print()

  mofi1 %>% 
    filter( pin==5529050722) %>%  
    filter( supply_date >= '2014-07-08') %>%  
    arrange( supply_date, item_code ) %>% 
    select( ci, Day_diff, Stnd_dose,quantity, ddd_mg_factor, unit_wt, everything()) %>%
    print()

rm(list=c('mofi','mofi1'))



  distinct( pin ) %>%
  count()

```
# multi day differences
```{r}

mofi1 %>% 
  filter( ci >= 0) %>% 
  { . } -> mofi_dd_multi

mofi_dd_multi %>% distinct( pin )

df_dd_overlap_combined  %>%
  distinct( pin) %>%
  bothDiff( mofi_dd_multi %>% distinct( pin), by=qc( pin))

 mofi_dd_multi %>% 
   anti_join( df_dd_overlap_combined , by=qc( pin) ) %>%
   distinct( pin, item_code ) %>%
   filter( !(item_code %in% c( '05339B', '01808E' )))


df_dd_overlap_combined %>% filter( pin == '61485')
mofi_dd_multi %>% filter( pin=='61485')


df %>% filter( pin == '61485') %>% arrange( pin, supply_date, item_code)
mofi1 %>% filter( pin=='61485') 

explore(5529050722)





explore = function( mpin ) {
  df %>% filter( pin == mpin ) %>% 
    arrange(pin, supply_date, item_code)  %>%
    print()
  mofi1 %>% filter( pin==mpin ) %>% print()

  df_dd_overlap_combined %>% filter( pin == mpin) %>% print()
  mofi_dd_multi %>% filter( pin==mpin) %>% print()
  FALSE
}


